Thesis: draft

### 2021-05-21 draft.tex
Update draft.tex
small change in Ch. 2 Watts-Strogatz

Perra and Rocha showed that a high clustering coefficient enhances the formation of echo chambers \cite{Perra2019}. Here, we will use the Watts-Strogatz model to investigate the interplay between high clustering and the presence of stubborn actors and we will use it as a comparison for networks that posses a community structure without having a high clustering coefficient. We will investigate whether community structure behaves similar to high clustering regarding the appearance of echo chambers. The Watts-Strogatz model is also used to build the constituent communities in the stochastic Watts-Strogatz block model.

>>>>

Perra and Rocha showed that high clustering enhances the formation of echo chambers \cite{Perra2019}. Here, we will use the Watts-Strogatz model to investigate the interplay between high clustering and the presence of stubborn actors and we will use it as a comparison for networks that posses community structure without having high clustering. We will investigate whether community structure behaves similar to high clustering regarding the appearance of echo chambers. The Watts-Strogatz model is also used to build the constituent communities in the stochastic Watts-Strogatz block model.
